Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis

### 2019-09-20 01_Meta-analysis_experiments.Rmd
updated information on maps corrected some code Removed obsolete information

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
library(dplyr)
library(readr)
library(kableExtra)
library(leaflet)
source("R/import_data.R")
```

@@

* 2013
   + Premer; no raw data
   + Milmerran; no raw data
   + Mt Mary; no raw data
   + Goolhi; no raw data

@@

**2013 Field trials**  
Fungicide treatments were described in reports in two letter acronyms.
The following is the assumed usage.

```{r}
knitr::kable(cbind(
   Acronym = c("SF", "Ti", "AX", "Ca"),
   `Expected Fungicide` = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
   `Active Ingredient` = c(
      "Sulphur",
      "Propiconazole",
      "Azoxystrobin and Cyproconazole",
      "Carbendazim"
   )
))
```

@@

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(e_treatment)),
   caption = "Description of Experiments"
) %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")

@@

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College"
   ),
   lat = c(-28.215 , -26.58, -27.56, -23.54),
   lon = c(152.1003, 151.83, 152.32, 148.19)
)

leaflet() %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)
```

>>>>

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
library(dplyr)
library(readr)
library(kableExtra)
library(leaflet)
library(htmltools)
source("R/import_data.R")
```

@@

* 2013  
   + Premer  
   + Milmerran   
   + Mt Mary   
   + Goolhi

@@

**2013 Field trials**  
Trials were conducted by the National Growers Alliance (NGA). The raw data were obtained from Lawrie Price. NGA data were formatted to be compliant with existing data rating and scales in the R script `Cleaning historical data.R`.

@@

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(n_treatment)),
   caption = "Description of Experiments"
 ) # %>%  #commented as was redering empty, needs a look in
#    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
#    scroll_box(width = "900px", height = "500px")

@@

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
      ),
   lat = c(-28.215 , -26.58, -27.56, -23.54, -27.51666, -31.43449, -27.923674, -31.0142, -31.00246, -27.905313, -27.564277),
   lon = c(152.1003, 151.83, 152.32, 148.19, 151.450,150.0052, 151.242706, 150.05018, 149.82507, 151.9772,151.867879)
)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
#   addPopups(lng = experiment_sites$lon, lat = experiment_sites$lat, popup = experiment_sites$location)
